Exploring the Utility of Machine Learning Across Varied Data Formats

### 2024-05-25 homework2/paper/paper.tex
write introduction for chapter 4

% ------------------------------------------------------------------------------
\section{Algorithms Designs}

>>>>

% ------------------------------------------------------------------------------
\section{Algorithms Designs}
Algorithm design is a critical aspect of computer science and machine learning, 
focusing on creating efficient and effective methods to solve complex problems. 
The process involves the careful selection of algorithms based on the specific 
characteristics of the data and the desired outcomes. This document explores the 
application of two prominent machine learning algorithms, Linear Regression and 
Multi-Layered Perceptron (MLP), on diverse datasets. The goal is to compare their 
performance and suitability for different types of prediction tasks, particularly 
in the contexts of stroke prediction and salary prediction.

\subsection{Linear Regression}
Linear Regression is one of the most fundamental and widely used algorithms in 
machine learning. It is known for its simplicity, interpretability, and 
efficiency in identifying linear relationships between variables. The primary 
purpose of Linear Regression is to model the relationship between a dependent 
variable and one or more independent variables by fitting a linear equation to 
observed data.

In the context of stroke prediction, Linear Regression can be used to analyze 
how various factors such as age, blood pressure, cholesterol levels, and smoking 
history influence the likelihood of experiencing a stroke. Its straightforward 
approach allows for clear insights into the significance and impact of each 
factor on stroke risk.

\subsection{Multi-Layered Perceptron (MLP)}
Multi-Layer Perceptron (MLP) is a type of artificial neural network designed to 
capture complex, non-linear patterns in data. Unlike Linear Regression, which is
limited to linear relationships, MLPs consist of multiple layers of interconnected 
nodes, or neurons, that can model intricate interactions between variables.

MLPs are particularly suitable for tasks involving complex datasets with 
non-linear relationships, such as salary prediction. In salary prediction, 
factors like education, work experience, industry sector, and other 
socio-economic variables interact in complex ways that Linear Regression might 
not fully capture. MLPs can learn these non-linear patterns, providing a more 
accurate and nuanced understanding of the factors influencing salary levels.
